---
title: "p8105_hw4_mp3652"
author: "MeOak Place"
date: "October 24, 2017"
output: html_document
---

```{r load_packages, warning = FALSE, message = FALSE}
library(tidyverse)
library(data.table)
library(dplyr)
library(devtools)
library(DT)
library(forcats)
library(ggplot2)
library(ggridges)
library(ggthemes)
library(haven)
library(janitor)
library(knitr)
library(magrittr)
library(readr)
library(readxl)
library(reshape2)
```

###################################

Problem 1:  Pups

###################################

getwd()
names(pups_data) #lists variable names
clean_names(pups_data) #lowercases variable names and tibbles data
tail(pups_data, 5) #last five
head(pups_data) #first six

```{r importing data, warning = FALSE, message = FALSE}
pups_data = read_csv(file = "./data/FAS_pups.csv") %>% 
  clean_names() %>% 
  select(-c(2)) %>%                             #removing sex column as key is n/a
  arrange(litter_number)
pups_data

length(unique(pups_data$id))

##############
# avg ears
##############
ears = pups_data %>%            
  select(-c(3:5)) %>% 
  group_by(litter_number) %>% 
  mutate(
    "avg_pd_ears" = round(mean(pd_ears), 1)
    ) %>% 
  select(-c(2)) %>% 
  filter(!duplicated(litter_number))
ears


##############
# avg eyes
##############
eyes = pups_data %>%                            
  select(-c(2, 4, 5)) %>% 
  group_by(litter_number) %>% 
  mutate(
    "avg_pd_eyes" = round(mean(pd_eyes), 1)
    ) %>% 
  select(-c(2)) %>% 
  filter(!duplicated(litter_number))
eyes


##############
# avg pivot
##############
pivot = pups_data %>%
  select(-c(2, 3, 5)) %>% 
  group_by(litter_number) %>% 
  mutate(
    "avg_pd_pivot" = round(mean(pd_pivot), 1)
    ) %>% 
  select(-c(2)) %>% 
  filter(!duplicated(litter_number))
pivot


##############
# avg walk
##############
walk = pups_data %>%
  select(-c(2:4)) %>% 
  group_by(litter_number) %>% 
  mutate(
    "avg_pd_walk" = round(mean(pd_walk), 1)
    ) %>% 
  select(-c(2)) %>% 
  filter(!duplicated(litter_number))
walk

pups = data.frame(ears, pivot, walk, eyes) %>% #no merge() b/c joining 4 df's, not 2
  mutate("id" = labels(litter_number)) %>%
  select(-c(1,3,5,7)) 
pups
```
############################################################################
The collaborator (Josie) will create a plot showing the distribution of post-natal days for each developmental landmark.
############################################################################

```{r Plot, warning = FALSE, message = FALSE}
#Josie's Collaboration
#ridge
pups %>%
  gather(key = landmark, value = average_days, avg_pd_ears:avg_pd_eyes) %>%
  ggplot(aes(y = landmark, x = average_days)) + geom_density_ridges() + 
  labs(
    title = "Average Days to Acheive Post-Natal Developmental Landmarks",
    x = "Average Days",
    y = "Developmental Landmark"
  )
```


<<<<<<< HEAD
=======
#The collaborator (Josie) will create a plot showing the distribution of post-natal days for each developmental landmark.
#########################################################################################################
pups %>%
  group_by(id) %>%
  ggplot(aes(x = ))
  
  
```
>>>>>>> 70cd31df7103dc1038afde52ff2475b988a3ea96
The original pups data set contained ___ observations; however, there were only `r length(unique(pups_data$id))` distinct litter numbers.  As such, we assumed that the multiple entries for each pup were a result of multiple observers, each of whom uniquely recorded developmental landmarks. 

unique litter numbers.  As such,  we assumed that developmental landmarks were recorded by multiple observers as reflected by the multiple entries and marginal differences in post-natal day.


############################################################################







############################################################################


############################################################################
In Problems 1 and 2, I worked with Josie Alford (UNI: jma2249).

### Problem 1

#The GitHub repo containing our solution to this problem is [here](https://github.com/meoak/p8105_hw4_mp3652)


### Problem 2

#The GitHub repo containing the solution to this problem is [here](https://github.com/josiealford14/p8105_hw4_jma2249)


### Problem 3

#My personal website is [here](http://meoakplace.com) ###need to set this up
###################################################################


###################################

Problem 2:  Five-thirty-eight

###################################


This problem uses the 538 datasets. 
Because this dataset is small and can be made public you should:
  include that data file in your directory for this problem, and 
    load that data file using relative paths.

The project lead will load and tidy the data for this problem. 
Combine the data in pols-month.csv and GDP.csv based on the date / month 
  (use lubridate::floor_date to collapse dates to the first day of the month).

The collaborator *MeOak* will create a plot showing the GDP value over time, 
  including the party of the president in an informative aesthetic.

The R Markdown document in your GitHub repository should 
  produce a file including code and text that explains the analyses and results for this problem.


###################################

Problem 3:  Personal Website

###################################

Create a personal website at <YOUR_GH_NAME>.github.io. This page can be as extensive as you’d like, but it should include at least:

A brief introductory landing page
A page giving your academic and professional experience (i.e. a resume)
Links in the site navigation for your GitHub account, your email, and any other professional networks.
